---
title: "Bivariate Normal Distribution"
author: "Ruiqi Li"
date: "October 26, 2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
```

## BVND Plot
Move the slider to change the plot

```{r eruptions, echo=FALSE}
inputPanel(
  sliderInput("mu1",
                   "mu1: ",
                   min = -20,
                   max = 20,
                   value = 0),
       
       sliderInput("mu2",
                   "mu2: ",
                   min = -20,
                   max = 20,
                   value = 0),
       
       sliderInput("s11",
                   "s11: ",
                   min = 0,
                   max = 20,
                   value = 10),
       
       sliderInput("s22",
                   "s22: ",
                   min = 0,
                   max = 20,
                   value = 10),
       
       sliderInput("rho",
                   "rho: ",
                   min = 0,
                   max = 1,
                   value = 0.5),
       
       checkboxInput("cm", "Show Covariance Matrix", TRUE)
)

renderPlotly({
    
    mu1 = input$mu1
    mu2 = input$mu2
    s11 = input$s11
    s22 = input$s22
    rho = input$rho
    
    x1  = seq(-20, 20, length = 41)
    x2 = x1
    
    bvnd = function(x1, x2) {
      term1<-1 / (2 * pi * sqrt(s11 * s22 * (1 - rho ^ 2)))
      term2<--1 / (2*(1 - rho ^ 2))
      term3<-(x1 - mu1) ^ 2 / s11
      term4<-(x2 - mu2) ^ 2 / s22
      term5<--2 * rho * ((x1 - mu1) * (x2 - mu2)) / (sqrt(s11) * sqrt(s22))
      term1 * exp(term2 * (term3 + term4 - term5))
    }
    
    z = outer(x1, x2, bvnd)
    plot_ly(x = x1, y = x2, z = z) %>% add_surface()
  })


renderPlotly({
    
    mu1 = input$mu1
    mu2 = input$mu2
    s11 = input$s11
    s22 = input$s22
    rho = input$rho
    
    x1  = seq(-20, 20, length = 41)
    x2 = x1
    
    bvnd = function(x1, x2) {
      term1<-1 / (2 * pi * sqrt(s11 * s22 * (1 - rho ^ 2)))
      term2<--1 / (2*(1 - rho ^ 2))
      term3<-(x1 - mu1) ^ 2 / s11
      term4<-(x2 - mu2) ^ 2 / s22
      term5<--2 * rho * ((x1 - mu1) * (x2 - mu2)) / (sqrt(s11) * sqrt(s22))
      term1 * exp(term2 * (term3 + term4 - term5))
    }
    
    z = outer(x1, x2, bvnd)
    plot_ly(z = z, type = "contour")
  })

renderPrint({
    mu1 = input$mu1
    mu2 = input$mu2
    s11 = input$s11
    s22 = input$s22
    rho = input$rho
    
    s12 <- rho * sqrt(s11) * sqrt(s22)
    if (input$cm == F) "Click on the checkbox to see the covariance" else s12
  })

renderPrint({
    d <- event_data("plotly_hover")
    if (is.null(d)) "Hover on a point!" else d
  })
  
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



